Self Regulation Ontology Retest Data Report

### 2017-04-25 SRO_Report.Rmd
fixed decimals

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(jsonlite)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(digits = 4)
```

@@

Average reliability metrics and the number of variables for both the surveys and the tasks
Both Spearman $\rho$'s as well the ICC's are higher for surveys.  
Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
```{r warning=FALSE, message=FALSE}
rel_df %>%
  group_by(task) %>%
  summarise(median_spearman = median(spearman),
            median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n())
```

@@

```{r}
datatable(rel_df, filter = 'top')
```

@@

```{r}
datatable(rel_df %>%
  filter(icc>(-0.1), icc<0.1) %>%
  arrange(icc))
```

@@

datatable(tmp)
```

@@

```{r warning=FALSE, message=FALSE}
datatable(measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
  group_by(measure_type) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            num_measures = n()) %>%
  arrange(-median_icc, -median_spearman))
```

@@

```{r warning=FALSE, message=FALSE}
datatable(tmp %>%
  group_by(label_1,label_2, label_3) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            n_vars = n()) %>%
  arrange(-median_icc, -median_spearman))
```

@@

```{r warning=FALSE, message=FALSE}
raw_rel_df %>%
  group_by(task) %>%
  summarise(median_spearman = median(spearman),
            median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n())
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(jsonlite)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(scipen = 1, digits = 4)
```

@@

Average reliability metrics and the number of variables for both the surveys and the tasks
Both Spearman $\rho$'s as well the ICC's are higher for surveys.  
Systematic differences between the two measurements ($\eta^2$) are higher for tasks than surveys (potentially indicating learning effects?).  
Unexpectedly, median standard error of measurement is higher for surveys but the distribution below suggests that this is a side effect of having too many task measures with very low SEMs.
```{r warning=FALSE, message=FALSE}
rel_df %>%
  group_by(task) %>%
  summarise(median_spearman = median(spearman),
            median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n()) %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc', 'median_eta_sq', 'median_sem'), digits=3)
```

@@

```{r}
rel_df %>%
  datatable(filter='top') %>%
  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
```

@@

```{r}
rel_df %>%
  filter(icc>(-0.1), icc<0.1) %>%
  arrange(icc) %>%
  datatable() %>%
  formatRound(columns=c('spearman', 'icc', 'eta_sq', 'sem'), digits=3)
```

@@

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
```

@@

```{r warning=FALSE, message=FALSE}
measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
  left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
  group_by(measure_type) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            num_measures = n()) %>%
  arrange(-median_icc, -median_spearman) %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
```

@@

```{r warning=FALSE, message=FALSE}
tmp %>%
  group_by(label_1,label_2, label_3) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            n_vars = n()) %>%
  arrange(-median_icc, -median_spearman) %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc'), digits=3)
```

@@

```{r warning=FALSE, message=FALSE}
raw_rel_df %>%
  group_by(task) %>%
  summarise(median_spearman = median(spearman),
            median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n()) %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc', 'median_eta_sq', 'median_sem'), digits=3)
```
